---
title: "mp3"
author: "Libby Leung, Madeleine Hickman, Kerry LeCure"
date: "11/13/2017"
output: html_document
---
Probelm Statement (need to rephrase): Genre Multiplicity: Prof. Keller explained how the labor model in Hollywood has changed over time, specifically with respect to the 1947 court decision that broke up the vertical integration of studios. Is it true that movies made today tend to have overlapping genres in a way that they did not in the past? Is is true that older movies tended to fit squarely in one genre, while more recent movies tend to span multiple genres? Is there a historical moment where this genre complexity begins? Does it have patterns of any discernible kind?
```{r, message=FALSE}
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
```
```{r}
db %>%
  dbGetQuery("SELECT *
             FROM info_type;")
db %>%
  dbGetQuery("SELECT * FROM kind_type;")
```
```{r}
db %>%
  dbGetQuery("SELECT *
             FROM movie_info
             WHERE info_type_id = 3
             LIMIT 10;")
```

```{r}
db %>%
  dbGetQuery("SELECT t.id, t.title, t.kind_id, t.production_year, mi.movie_id, mi.info_type_id, mi.info
             FROM title t
             JOIN movie_info mi ON mi.movie_id = t.title
             WHERE mi.info_type_id = 3 AND t.kind_id = 1
             LIMIT 1000;")
```

github respository link: https://github.com/kerrylecure/sds192-mp3